---
title: "ETC5510: Introduction to Data Analysis"
week: "Week 9, part B"
subtitle: "Creating a dashboard"
author: "Stuart Lee"
email: ""
date: "May 2020"
pdflink: ""
bgimg: "images/bg1.jpg"
output:
  xaringan::moon_reader:
    css:
      - ninjutsu 
      - "assets/animate.css"
      - "assets/monash-logo.css"
      - "assets/monash-brand.css"
      - "assets/monash-fonts.css"
      - "assets/styles.css" # small improvements
      - "assets/custom.css" # add your own CSS here!
      - "assets/demo.css" # this should be removed
    self_contained: false 
    seal: false 
    chakra: 'libs/remark-latest.min.js'
    lib_dir: libs
    includes:
      in_header: "assets/custom.html"
    mathjax: "assets/mathjax-local/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
    nature:
      highlightStyle: github 
      highlightLanguage: r 
      highlightLines: true
      highlightSpans: false 
      countIncrementalSlides: false
      slideNumberFormat: '%current%/%total%'
      navigation:
        scroll: false 
        touch: true
        click: false
      ratio: '16:9'
---
  
```{r titleslide, child="components/titleslide.Rmd"}
```


---

There are some short explanatory youtube videos. Here is  my recommended list, in  recommended order of viewing. 
Sharon  Machlis
R language tip: Easy dashboards with flexdashboard https://www.youtube.com/watch?v=_oDfBVr9wmQ
Jonathan Ng's series, has many, but its hard to navigate. I suggest these ones.
- 5 Minute Dashboard with R Shiny Flex Dashboards https://www.youtube.com/watch?v=45h71BFbL1w: Getting set up with shiny, to have inputs and reactive plots. Uses an igraph example.
- Flexdashboard Cheat Sheet https://www.youtube.com/watch?v=gkQvhMA24ig: Layout explanations. Nice style of making  changes and exploring the result
- Dyanmic Dashboard Filters with R, Shiny Flex Dashboards https://www.youtube.com/watch?v=MBNdyRQIvE4:  Reasonable getting  started with shiny elements.
- Build a Dashboard in 10 Seconds with R Shiny Flexdashboard https://www.youtube.com/watch?v=6WTaGEOVJ6s: Advanced R coding. Starts from a sample flexdashboard with inputs  and  reactives, and adds more advanced elements to it. (Follows Dyanmic Dashboard Filters with R, Shiny Flex Dashboards)
- Load R Shiny Flexdashboards Faster https://www.youtube.com/watch?v=MlfHf8PpX5E&

---
  
```{r endslide, child="components/endslide.Rmd"}
```
