---
title: "ETC5510: Introduction to Data Analysis"
week: "Week 8, part B"
subtitle: "Text analysis Part 2"
author: "Nicholas Tierney & Stuart Lee"
email: "ETC5510.Clayton-x@monash.edu"
date: "May 2020"
pdflink: ""
bgimg: "images/bg1.jpg"
output:
  xaringan::moon_reader:
    css:
      - ninjutsu 
      - "assets/animate.css"
      - "assets/monash-logo.css"
      - "assets/monash-brand.css"
      - "assets/monash-fonts.css"
      - "assets/styles.css" # small improvements
      - "assets/custom.css" # add your own CSS here!
      - "assets/demo.css" # this should be removed
    self_contained: false 
    seal: false 
    chakra: 'libs/remark-latest.min.js'
    lib_dir: libs
    includes:
      in_header: "assets/custom.html"
    mathjax: "assets/mathjax-local/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
    nature:
      highlightStyle: github 
      highlightLanguage: r 
      highlightLines: true
      highlightSpans: false 
      countIncrementalSlides: false
      slideNumberFormat: '%current%/%total%'
      navigation:
        scroll: false 
        touch: true
        click: false
      ratio: '16:9'
---
  
```{r titleslide, child="components/titleslide.Rmd"}
```


```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(tidytext)
opts_chunk$set(echo = TRUE,   
               message = FALSE,
               warning = FALSE,
               collapse = TRUE,
               fig.height = 4,
               fig.width = 8,
               fig.align = "center",
               fig.retina = 2,
               cache = FALSE)

theme_set(theme_bw())
as_table <- function(...) knitr::kable(..., format='html', digits = 3)
```

---
class: refresher

# Recap 

- tidying up text
- stop_words - (I, am, be, the, this, what, we, myself)

---
# Overview

- tidy text continued

---
class: transition
# Sentiment analysis

Sentiment analysis tags words or phrases with an emotion, and summarises these, often as the positive or negative state, over a body of text. 

---
# Sentiment analysis: examples

- Examining effect of emotional state in twitter posts
- Determining public reactions to government policy, or new product releases
- Trying to make money in the stock market by modeling social media posts on listed companies
- Evaluating product reviews on Amazon, restaurants on zomato, or travel options on TripAdvisor

---
# Lexicons

The `tidytext` package has a lexicon of sentiments, based on four major sources: [AFINN](http://www2.imm.dtu.dk/pubdb/views/publication_details.php?id=6010), [bing](https://www.cs.uic.edu/~liub/FBS/sentiment-analysis.html), [Loughran](https://sraf.nd.edu/textual-analysis/resources/#LM%20Sentiment%20Word%20Lists), [nrc](http://saifmohammad.com/WebPages/NRC-Emotion-Lexicon.htm)

---
# emotion

What emotion do these words elicit in you?

- summer
- hot chips
- hug
- lose
- stolen
- smile

---
# Different sources of sentiment

- The `nrc` lexicon categorizes words in a binary fashion ("yes"/"no") into categories of positive, negative, anger, anticipation, disgust, fear, joy, sadness, surprise, and trust. 
- The `bing` lexicon categorizes words in a binary fashion into positive and negative categories. 
- The `AFINN` lexicon assigns words with a score that runs between -5 and 5, with negative scores indicating negative sentiment and positive scores indicating positive sentiment.

---

# Different sources of sentiment
```{r get-sentiment-afinn}
get_sentiments("afinn")
```

---
# Sentiment analysis

- Once you have a bag of words, you need to join the sentiments dictionary to the words data. 
- Particularly the lexicon `nrc` has multiple tags per word, so you may need to use an "inner_join". 
- `inner_join()` returns all rows from x where there are matching values in y, and all columns from x and y. 
- If there are multiple matches between x and y, all combination of the matches are returned.

---
# Exploring sentiment in Jane Austen

`janeaustenr` package contains the full texts, ready for analysis for for Jane Austen's 6 completed novels: 

1. "Sense and Sensibility"
2. "Pride and Prejudice"
3. "Mansfield Park"
4. "Emma"
5. "Northanger Abbey"
6. "Persuasion"


---
# Exploring sentiment in Jane Austen

```{r show-jane-austen}
library(janeaustenr)
library(stringr)

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, 
                                     regex("^chapter [\\divxlc]", 
                                           ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```

---

# Exploring sentiment in Jane Austen
```{r print-tidy-ooks}
tidy_books
```

---
# Count joyful words in "Emma"

```{r count-joy}
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```

---
# Count joyful words in "Emma"

"Good" is the most common joyful word, followed by "young", "friend", "hope". 

All make sense until you see "found". 

Is "found" a joyful word?

---
# Comparing lexicons

.pull-left[
- All of the lexicons have a measure of positive or negative. 
- We can tag the words in Emma by each lexicon, and see if they agree. 
]

.pull-right[
```{r compare-sentiments}
nrc_pn <- get_sentiments("nrc") %>% 
  filter(sentiment %in% c("positive", 
                          "negative"))

emma_nrc <- tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_pn)

emma_bing <- tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(get_sentiments("bing")) 

emma_afinn <- tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(get_sentiments("afinn"))
```
]

---
# Comparing lexicons

```{r show-lexi} 
emma_nrc
```

---
# Comparing lexicons

```{r show-lexi-afinn} 
emma_afinn
```


---
# Comparing lexicons

```{r compare-sentiments-show}
emma_nrc %>% count(sentiment) %>% mutate(n / sum(n))

emma_bing %>% count(sentiment) %>% mutate(n / sum(n))
```

---
# Comparing lexicons

```{r compare-sentiments-more}
emma_afinn %>% 
  mutate(sentiment = ifelse(value > 0, 
                            "positive", 
                            "negative")) %>% 
  count(sentiment) %>% 
  mutate(n / sum(n))

```

---
class: transition
# Your Turn: Sentiment of Austen

- What are the most common "anger" words used in Emma?
- What are the most common "surprise" words used in Emma?
- Which book is the most positive? negative?
- Using your choice of lexicon (nrc, bing, or afinn) compute the proportion of positive words in each of Austen's books.

---
# Lab exercise: The Simpsons

Data from the popular animated TV series, The Simpsons, has been made available on [kaggle](https://www.kaggle.com/wcukierski/the-simpsons-by-the-data/data). 

- `simpsons_script_lines.csv`: Contains the text spoken during each episode (including details about which character said it and where)
- `simpsons_characters.csv`: Contains character names and a character id

---
# Lab exercise (bonus) Origin of Species

- Downloading books from gutenberg
- Using tf-idf to look at how editions of the Darwin's book have changed

---
  
```{r endslide, child="components/endslide.Rmd"}
```
