---
title: "ETC5510: Introduction to Data Analysis"
subtitle: "Semester 1 2020"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
library(tidyverse)
library(knitr)
library(kableExtra)
library(glue)
library(googlesheets4)
library(lubridate)
library(ymlthis)
library(yaml)


monash_pals <- c(blue = "#4269a5",
                 purple = "#8e4f89", 
                 green = "#39825a", 
                 orange = "#dc6141")
```

```{r functions}
generate_readings <- function(week, part){
  readings <- read_yaml("materials/readings.yml")
  reading_list <- glue('readings[["Week {week}"]]\\
                                      [["Readings"]]\\
                                      [["{part}"]]')
  eval(parse(text = reading_list)) %>% 
    glue_collapse("\n\n")
}

```

- Lecturer: Stuart Lee
- Chief Examiner: Di Cook
- Tutors: Steph Kobakian, Sherry Zhang

This is the course website. This page shows information about the consultation times, MoVE, and Schedule and lecture notes.

The "Assessments" tab above provides information about all assessment for ETC5510.

## Expectations 

- Unless your question is a personal issue or an administrative matter, please do not send us direct email. The [ED site](https://edstem.org/) is appropriate for questions related to the course material.
- For personal or administrative issues, the email contact is: ETC5510.Clayton-x@monash.edu
- ED is used for asking for help, reading and lab exercise quizzes and assignment turn in. Only your name and email is stored in this system.
- **If you register after the start of the semester** or if you
  miss a lecture/lab, it is your responsibility to catch up with
  missed material, learn about due dates for material to be turned in,
  and getting assigned to a group for team work.

## Consultation times

Consultations begin from Week 2 (16th March)

- Steph Kobakian: TBA
- Sherry Zhang: Friday 2pm-3pm
- Stuart Lee: Monday afternoon **Menzies W1105**
- Stuart Lee: Wednesday afternoon **Menzies W1105**

## Tentative Schedule

There are two lectorials every week:

* **Monday 6-8pm** (Room 321 - LTB Bldg 92)
* **Wednesday 6 - 8pm** (Room 321 - LTB Bldg 92)

There are no lectorials during the midsemester break.

```{r read-create-sheet, eval = FALSE}
# to be run interatively when google sheet is updated
google_schedule <- read_sheet("https://docs.google.com/spreadsheets/d/1YkHiIwPxJbmWdsnjow_ju59QIwJVMMZEcWzqARpCkco/edit?usp=sharing")

write_csv(google_schedule, path = "materials/schedule.csv")
```


```{r read-data-google}
schedule <-  read_csv("materials/schedule.csv") %>% 
  mutate(Slides = case_when(
    !is.na(HTML) & !is.na(PDF) ~ glue("<a class='fa fa-link' href='slides/{HTML}'></a> <a class='fa fa-file-pdf' href='slides/{PDF}'></a>"),
    !is.na(HTML) ~ glue("<a class='fa fa-link' href='slides/{HTML}'></a>"),
    !is.na(PDF) ~ glue("<a class='fa fa-file-pdf' href='slides/{PDF}'></a>"),
    TRUE ~ ""
  ),
  Exercise = case_when(
    !is.na(Exercise) ~ glue("<a class='fa fa-link' href='{Exercise}'></a>"),
    TRUE ~ ""
  ),
  Topic = ifelse(is.na(Topic), "", Topic),
  Exercise = ifelse(is.na(Exercise), "", Exercise)) %>% 
  # Date = janitor::excel_numeric_to_date(Date)) %>% 
  select(Week, 
         Lecture, 
         Date, 
         Slides, 
         Topic, 
         Exercise, 
         Readings, 
         Assessment) %>% 
  # generate readings
  mutate(Readings = map2_chr(Week, Lecture, generate_readings)) 

midsem_break <- 10 # after which week (but there are 2 lectures per week)

schedule %>% 
  kable(escape = FALSE, 
        align = c("c", "c", "c", "c", "l", "l")) %>% 
  kable_styling(bootstrap_options = "striped",
                fixed_thead = T) %>% 
  column_spec(1, width = "0.5cm") %>% 
  column_spec(2, width = "1cm") %>% 
  column_spec(3, width = "3cm") %>% 
  column_spec(4, width = "1cm") %>% 
  group_rows(group_label = "Midsemester Break", 
             start_row = midsem_break + 1, 
             end_row = midsem_break, 
             label_row_css = "background-color: #d9e1e8;") %>% 
  add_indent(1:midsem_break) %>%  # this needs to be done to match up with above
  add_indent((midsem_break+1):24) # this needs to be done to match up with above
```



