---
title: '"Origin of Species"'
author: "Stuart Lee"
date: "12/05/2020"
output: html_document
---

---
# Getting some books to study

The [Gutenberg project](http://www.gutenberg.org/wiki/Main_Page) provides the text of over 57000 books free online. 

Let's explore The Origin of the Species by Charles Darwin using the `gutenbergr` R package.

We need to know the `id` of the book, which means looking this up online anyway. 
- The first edition is `1228`
- The sixth edition is `2009`

---
# Packages used

- We need the `tm` package to remove numbers from the page, and `gutenbergr` to access the books.

```{r load-extra-pkgs}
# The tm package is needed because the book has numbers
# in the text, that need to be removed, and the
# install.packages("tm")
library(tidyverse)
library(tidytext)
library(tm)
library(gutenbergr)
```

# Download darwin

```{r download-darwin}
darwin1 <- gutenberg_download(1228)
darwin1
# remove the numbers from the text
darwin1$text <- removeNumbers(darwin1$text)
```


# Tokenize

- break into one word per line
- remove the stop words
- count the words
- find the length of the words

```{r tokenize-text}
stop_words <- get_stopwords()

darwin1_words <- darwin1 %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
  mutate(len = str_length(word))

darwin1_words
```



```{r analyse-text}
ggplot(darwin1_words, aes(x = n)) +
  geom_histogram(fill = "midnightblue")
```


```{r gg-analyse-text, eval = FALSE}
darwin1_words %>%
  top_n(n = 20, wt = n) %>%
  ggplot(aes(x = n,
             y = fct_reorder(word, n))) +
  geom_point() +
  ylab("")
```  

---
# Download and tokenize the 6th edition.

```{r dl-second-edition}
darwin6 <- gutenberg_download(2009)

darwin6$text <- removeNumbers(darwin6$text)
```

---
# show tokenized words

```{r table-second-edition}
darwin6_words <- darwin6 %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
  mutate(len = str_length(word))

darwin6_words
```

---
# show tokenized words
```{r quantile-second-edition}
ggplot(darwin6_words, aes(x = n)) +
  geom_histogram(fill = "midnightblue")
```

---
# show tokenized words
```{r gg-second-edition}
darwin6_words %>%
  top_n(n = 20,
        wt = n) %>%
  ggplot(aes(x = n, y = fct_reorder(word, n))) + geom_point() +
  ylab("")
```

---
# Compare the word frequency

.left-code[
```{r full-join-darwin}
darwin <- full_join(
  darwin1_words, 
  darwin6_words, 
  by = "word"
  ) %>%
  rename(
    n_ed1 = n.x, 
    len_ed1 = len.x, 
    n_ed6 = n.y, 
    len_ed6 = len.y
  )
```

---
# plot the word frequency

```{r plot-word-freq, eval = FALSE}
ggplot(darwin, 
            aes(x = n_ed1, 
                y = n_ed6, 
                label = word)) +
  geom_abline(intercept = 0, 
              slope = 1) +
  geom_point(alpha = 0.5) +
  xlab("First edition") + 
  ylab("6th edition") +
  scale_x_log10() + 
  scale_y_log10() + 
  theme(aspect.ratio = 1)
```


# Book comparison

Idea: Find the important words for the content of each document by decreasing the weight of commonly used words and increasing the weight for words that are not used very much in a collection or corpus of documents.

# Term frequency, inverse document frequency (`tf_idf`).

Helps measure word importance of a document in a collection of documents.

Recall:

$$ tf\_idf(w, d, \mathcal{D}) = tf(w,d) \times idf(w, \mathcal{D})$$


# Bind the editions:
```{r bind-rows-darwin}
darwin <- bind_rows("first" = darwin1_words, 
                    "sixth" = darwin6_words,
                    .id = "edition")

darwin
```

# Compute tf-idf

```{r darwin-tf-idf}
darwin_tf_idf <- darwin %>% 
  bind_tf_idf(word, edition, n)

darwin_tf_idf %>% 
  arrange(desc(tf_idf))
```

# Plot the results for top words

```{r gg-rawin-tf-idf, echo = FALSE}
gg_darwin_1_vs_6 <-
darwin_tf_idf %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word,
                       levels = rev(unique(word)))) %>%
  group_by(edition) %>%
  top_n(15) %>%
  ungroup() %>%
  ggplot(aes(x = word, 
             y = tf_idf, 
             fill = edition)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, 
       y = "tf-idf") +
  facet_wrap(~edition, 
             ncol = 2, 
             scales = "free") +
  coord_flip() + 
  scale_fill_brewer(palette = "Dark2")
```  


```{r gg-rawin-tf-idf-out, echo = FALSE}
gg_darwin_1_vs_6
```


- Mr Mivart appears in the 6th edition, multiple times

```{r show-mivart}
str_which(darwin6$text, "Mivart")
darwin6[5435, ]
```

# What do we learn?

- Prof title is used more often in the 6th edition
- There is a tendency for latin names 
- Mistletoe was mispelled in the 1st edition


# Your turn: Lab Comparing Darwin

- Does it look like the 6th edition was an expanded version of the first?
- What word is most frequent in both editions?
- Find some words that are not in the first edition but appear in the 6th.
- Find some words that are used the first edition but not in the 6th.
- Using a linear regression model find the top few words that appear more often than expected, based on the frequency in the first edition. Find the top few words that appear less often than expected.