---
title: "The Simpson's"
author: "YOUR NAME"
output: html_document
---

# The Simpsons
```{r read-scripts}
scripts <- read_csv("data/simpsons_script_lines.csv")
chs <- read_csv("data/simpsons_characters.csv")
sc <- left_join(scripts, chs, by = c("character_id" = "id"))
sc
```


## Count the number of times a character speaks

```{r count-names}
sc %>% 
  count(---, sort = TRUE)
```

## Are there missing names
```{r explore-missing}
sc %>% 
  filter(---)
```

## Pre-process the text
```{r process-simpsons-s1}
# steps 1. unnest tokens for spoken words
# step 2. remove stop words
sc_long <- sc %>%
  unnest_tokens(---) %>% 
  anti_join(---)
```


## Count the words

```{r process-simpsons-s3}
sc_words <- sc_long %>%
  count(---, sort = TRUE) %>%
  # remove any missing words
  filter(---)
```


## Plot the top 20 spoken words
```{r process-simpsons-s4}
sc_words %>% 
  top_n(20, wt = n) %>% 
  ggplot(aes(x = fct_reorder(word, ---), y = n)) +
  geom_col() +
  labs(x = '', 
       y = 'count', 
       title = 'Top 20 words') +
  coord_flip() 
```


# Tag the words with sentiments

Count words spoken by each character

```{r tag-sentiments}
sc_word_by_character <- sc_long %>% 
  count(---, word) %>%
  filter(!is.na(word))
```


Using AFINN words will be tagged on a negative to positive scale of -5 to 5.


```{r tag-sentiments2}
sc_s <- sc_word_by_character %>% 
  inner_join(get_sentiments("afinn"), by = "word")
sc_s
```

Compute the mean sentiment for each character.

```{r summarise-simpsons-characters}
sc_s %>% 
  group_by(name) %>% 
  summarise(---) %>% 
  arrange(desc(m))
```

# Focus on the main characters, instead of all characters.

Keep characters that have spoken at least 999 words.

```{r keep-main-chars}
keep <- sc %>% count(name, 
                     sort=TRUE) %>%
  filter(!is.na(name)) %>%
  filter(n > 999)

```

Re-compute the sentiment after removing unimportant characters:

```{r main-characters}
sc_s %>% 
  filter(name %in% keep$---) %>% 
  group_by(name) %>% 
  summarise(---) %>% 
  arrange(m)
```


## Exercises

1. Bart Simpson is featured at various ages. How has the sentiment of his words changed over his life?
2. Repeat the sentiment analysis with the NRC lexicon. What character is the most "angry"? "joyful"?
