---
title: "9a-class-network"
author: "Your Name"
date: "17/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# you have to install this from github
# run: remotes::install_github("sctyner/geomnet")
library(geomnet)
library(janitor)
```

```{r class-names}
class_names <- read_csv(here::here("data/class_names.csv")) %>% clean_names()

class_names
```


```{r class-names-graph}
ggplot(class_names, aes(from_id = s1_name, to_id = s2_name)) +
  geom_net(layout.alg = "kamadakawai",
    size = 2, 
    labelon = TRUE, 
    vjust = -0.6, 
    directed = FALSE, 
    fontsize = 3) +
  theme_net()
```


- Try changing the layout method to "circle" or "mds"
- Try setting a random seed, a random number that affects the initial condition for the layout optimisation. You coulde use code like this, substituting in a different number:

```{r}
set.seed(---)
```


- For the class members/tutors, shevin, james, nicole, wai, jamesjing, write out the 5x5 association matrix.

```{r}
class_names_subset <- class_names %>%
  ___(s1_name %in% c(___, ___))

class_names_subset
```


- try exploring the other datasets in the `geomnet` package:

```{r}
?geomnet::bikes
?geomnet::blood
?geomnet::email
```


