---
title: "9a-cross-rates"
author: "your name"
date: "17/05/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(geomnet)
```


```{r}
rates <- read_csv("data/rates_new.csv")
# remove duplicate rows
rates <- rates %>% 
  distinct() %>%  
  arrange(date)
```

## Your turn - plotting cross rate time series

Make some plots (or google) to answer these questions

- Is the NZD more similar to AUD, EUR, or JPY? (What currency is NZD?)
- Is SGD more similar to AUD, EUR, or JPY? (What currency is SGD?)

- How many currencies are there in the British Isles? 


## Remove relatively stable currencies

```{r pivot-cv}
# Compute coefficient of variation. We will only analyse 
# currencies that have changes substantially over this time.
cv <- function(x){
  sd(x)/mean(x)
}

rates_long <- rates %>% 
  pivot_longer(cols = -date, names_to = "currency") 

rates_cv <- rates_long %>% 
  group_by(currency) %>% 
  summarise(cv = cv(value)) 
```

### Your turn

- compute a five number summary of the CV values over all currencies
- create a new table called `rates_stable` that has cv less than
its first quantile
- remove low quantile currencies from `rates_long` using an anti
join save the results to a new object called `rates_sub`
- Some of the currencies ... aren't really currencies. Google these ones: XAG, XDR, XPT - what are they?
- Remove the not currencies from `rates_sub` using `filter()`.


## Standardising columns

Using group by and mutate!

```{r rescale}
scale01 <- function(x) (x - mean(x)) / sd(x)

rates_scaled <- rates_dropped %>%
  group_by(currency) %>% 
  mutate(value = scale01(value))
```

### Your turn

- Make a plot of the AUD vs the SGD (using the standardised units). Do they look like they are trending together?

- How does this compare to the network layout?
- Starting from the code block below, construct a network layout
from a distance matrix:

```{r}
rates_wide <- rates_scaled %>% 
    pivot_wider(id_cols = "date", names_from = "currency") %>%
    select(-date)

# compute distance between currencies, rows <--> columns 
rates_wide_t <- t(rates_wide)

currency_dist <- as.matrix(dist(rates_wide_t, 
                             diag = TRUE, 
                             upper = TRUE))
distance_tbl <-  currency_dist %>% 
  as.data.frame() %>%
  rownames_to_column(var = "from_currency") %>% 
  pivot_longer(-from_currency, 
               names_to = "to_currency",
               values_to = "distance")
```

- Remember you want to filter out rows when from and to are the same
- And filter out currencies that are "far" away from each other

- Here's a starter to help you visualise the network

```{r network}
library(geomnet)
set.seed(10052016)
ggplot(data = ---, 
       aes(
         from_id = from_currency, 
         to_id = to_currency
         )) +
  geom_net(
    layout.alg = "kamadakawai",
    size = 2, 
    labelon = TRUE, 
    vjust = -0.6, 
    ecolour = "grey60",
    directed = FALSE, 
    fontsize = 3, 
    ealpha = 0.5
    ) +
    theme_net() +
    theme(
      legend.position = "bottom"
      )
```


