---
title: "The books of Jane Austen"
author: "Your Name"
output: html_document
---

```{r setup}
library(tidyverse)
library(tidytext)
```

In this lab exercise we will analyse the sentiment of Austen's books. 

Below is the code to tokenise the books and add line numbers and chapters.

```{r tidy-books}
library(janeaustenr)

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, 
                                     regex("^chapter [\\divxlc]", 
                                           ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```

Add sentiment categories to all the books using the nrc lexicon.

```{r nrc}
nrc <- get_sentiments("nrc")
```


- What are the most common "anger" words used in Emma?
- What are the most common "surprise" words used in Emma?

```{r}
tidy_books %>% 
  filter()
  ...
```


Using another lexicon (bing, or afinn) compute the proportion of 
positive words in each of Austen's books.

- Which book is the most positive? negative?

```{r}
# add code for next lexicon here
```